Clustering SCPCL000822 and SCPCL000824

### 2024-08-02 analyses/cell-type-ewings/exploratory_analysis/05-cluster-exploration.Rmd
add id to title and render

  ggplot(plot_df, aes(x = nn_param, y = {{ stat_column }})) +
    # ggforce::geom_sina(size = .2) +
    ggbeeswarm::geom_quasirandom(method = "smiley", size = 0.1) +
    stat_summary(
      aes(group = nn_param),
      color = "red",
      # median and quartiles for point range
      fun = "median",
      fun.min = function(x) {
        quantile(x, 0.25)
      },
      fun.max = function(x) {
        quantile(x, 0.75)
      }
    )
}

>>>>

  ggplot(plot_df, aes(x = nn_param, y = {{ stat_column }})) +
    # ggforce::geom_sina(size = .2) +
    ggbeeswarm::geom_quasirandom(method = "smiley", size = 0.1) +
    stat_summary(
      aes(group = nn_param),
      color = "red",
      # median and quartiles for point range
      fun = "median",
      fun.min = function(x) {
        quantile(x, 0.25)
      },
      fun.max = function(x) {
        quantile(x, 0.75)
      }
    ) +
    labs(title = id)
}
